# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data

```{r, warning=FALSE, }
df <- read.csv("activity.csv")
library(plyr)
library(ggplot2)
library(reshape2)
```

## What is mean total number of steps taken per day?
```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.height=6, fig.width=8}
df1 <- ddply(df, .(date), summarise, total = sum(steps, na.rm=T))
df1_mean <- mean(df1$total)
df1_median <- median(df1$total)
ggplot(df1, aes(x=as.Date(date), y=total)) +geom_bar(stat="identity")
```

The mean total number of steps taken per day is `r df1_mean` and the median is `r df1_median`

## What is the average daily activity pattern?
```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.height=6, fig.width=8}
df2 <- ddply(df, .(date), mutate, average = mean(steps, na.rm=T))
ggplot(df2,aes(x=as.Date(date), y=average)) + geom_line() + xlab("Time") + ylab("Average Step per Day")

df1_max <-df1[df1$total == max(df1$total), ]
df1_max_date <- as.Date(df1_max[1,1])
df1_max_step <- as.vector(df1_max[1,2])

```
The `r df1_max_date` contains the maxium steps `r df1_max_step`.

## Imputing missing values

```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.height=6, fig.width=8}
# Count NA
totalNA <- sum(is.na(df[,1])) 

#Using mean of all the data to replace NA

df_new <-df
df_new$steps[is.na(df_new$step)] <- mean(df_new$steps, na.rm=T)


# Calculate mean and median of the new data frame
df3_sum <- ddply(df_new, .(date), summarise, totalsteps = sum(steps, na.rm=T))
df3_mean <- mean(df3_sum$totalsteps)
df3_median <- median(df3_sum$totalsteps)

ggplot(df3_sum, aes(x=as.Date(date), y=totalsteps)) + geom_bar(stat="identity") 

```
The total NA in data set is `r totalNA`. The mean total number of steps taken per day is `r df3_mean` and the median is `r df3_median`. They are different than old data set.

## Are there differences in activity patterns between weekdays and weekends?

```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.height=6, fig.width=8}

df_new$date <-weekdays(as.Date(df_new$date))
df_new$date <- ifelse(df_new$date =="Saturday"|df_new$date =="Sunday", 
                      "Weekend", "workday")

df_new$interval <-as.factor(df_new$interval)
df4 <-ddply(df_new, .(interval, date), 
            summarise, steps=mean(steps))
ggplot(df4, aes(x = interval, y = steps, group=date)) + 
    geom_line() + 
    facet_wrap(~date, nrow=2) + 
    scale_x_discrete(breaks=c(0, 500, 1000, 1500, 2000)) 
```
